Revisiting Multi-Domain Machine Translation

### 2020-08-27 2020/tacl2020/multidomain.tex
revised conclusion

\section{Conclusion and outlook \label{sec:conclusion}}
\fyDone{Write conclusions}\fyFuture{no mixture of experts}
In this study, we have carefully reconsidered the idea of multi-domain machine translation, which seems to be taken for granted in many recent studies. We have spelled out the various motivations for building such systems and the associated expectations in terms of system performance. We have then designed a series of requirements that MDMT systems should meet, and proposed a series of test procedures. In our experiments with a representative sample of MDMTs, we have found that most requirements were hardly met for our experimental conditions. If MDMT systems are able to outperform the mixed-domain baseline, at least for some domains, they all fall short to match the performance of fine-tuning on each individual domain, which remains the best choice in multi-source single domain adaptation.
% In this scenario, architecture-based strategies aimed at parameter sharing and/or representation normalization obtain the best results.\fyDone{Mitigate this}
As expected however, MDMTs are less brittle than fine-tuning when domain frontiers are uncertain, and can, to a certain extend, dynamically accommodate additional domains, this being especially easy for feature-based methodologies. Our experiments finally suggest that all methods show decreasing performance when the number of domains or the diversity of the domain mixture increases. % (for a fixed data size).

>>>>

\section{Conclusion and outlook \label{sec:conclusion}}
\fyDone{Write conclusions}\fyFuture{no mixture of experts}
In this study, we have carefully reconsidered the idea of multi-domain machine translation, which seems to be taken for granted in many recent studies. We have spelled out the various motivations for building such systems and the associated expectations in terms of system performance. We have then designed a series of requirements that MDMT systems should meet, and proposed a series of test procedures. In our experiments with a representative sample of MDMTs, we have found that most requirements were hardly met for our experimental conditions. If MDMT systems are able to outperform the mixed-domain baseline, at least for some domains, they all fall short to match the performance of fine-tuning on each individual domain, which remains the best choice in multi-source single domain adaptation.
\revisiondel{In this scenario, architecture-based strategies aimed at parameter sharing and/or representation normalization obtain the best results.}\fyDone{Mitigate this}
As expected however, MDMTs are less brittle than fine-tuning when domain frontiers are uncertain, and can, to a certain extend, dynamically accommodate additional domains, this being especially easy for feature-based methodologies. Our experiments finally suggest that all methods show decreasing performance when the number of domains or the diversity of the domain mixture increases. % (for a fixed data size).
